Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-03-31 ProbabilisticCoherence.tex
Cleaned Definition 3.1 using mathfrak for spaces since C looks like  complex numbers and N like natural

\documentclass[a4paper, 11pt]{article}
\usepackage{monashwp}
\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx}
\usepackage{mathrsfs, float, booktabs,todonotes}
\usepackage[bb=boondox]{mathalfa}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\hypersetup{citecolor=blue,linkcolor=blue,urlcolor=blue}
\DeclareNameAlias{sortname}{last-first}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcolumntype{L}{>{$}l<{$}} % math-mode version of "l" column type
\def\mathbi#1{\textit{ #1}}
\def\mathB#1{\textbf{ #1}}
\def\E{\text{E}}
\mathtoolsset{showonlyrefs=true}

@@

While coherent point forecasts have been discussed many times previously, the definitions of coherence previously given are vague and are not easily extended to the situation of probabilistic forecasting.

We first give a new definition for coherent point forecasts using the properties of vector spaces, and then provide a definition of coherent probabilistic forecasts.

\begin{definition}[Coherent subspace]
Suppose an $n$-dimensional time series $\bm{y}_t \in \mathbb{R}^n$ is subject to the linear aggregation constraint $\bm{y}_t = \bm{S}\bm{b}_t$, where $\bm{b}_t \in \mathbb{R}^m$ and $\bm{S}$ is an $n \times m$ constant matrix. Let $\mathbb{C}^m$ be an $m$-dimensional subspace of $\mathbb{R}^n$, where $\mathbb{C}^m < \mathbb{R}^n$. Then $\mathbb{C}^m$ is said to be a coherent space if it is spanned by the columns of $\bm{S}$. 
\end{definition}

Notice that the coherent space $\mathbb{C}^m$ is equivalent to the column space of $\bm{S}$, which we denote by $\mathscr{C}(\bm{S})$. Further, the space orthogonal to $\mathbb{C}^m$ is equivalent to the null space of $\bm{S}$, which we denote by $\bm{\mathbb{N}}^{n-m}$.

>>>>

\documentclass[a4paper, 11pt]{article}
\usepackage{monashwp}
\usepackage{amssymb, qtree, bm, multirow, textcmds, siunitx}
\usepackage{mathrsfs, float, booktabs,todonotes}
\usepackage[bb=boondox]{mathalfa}
\usepackage{tikz}
\usetikzlibrary{arrows,positioning,shapes,fit,calc}
\usepackage{amsfonts}
\hypersetup{citecolor=blue,linkcolor=blue,urlcolor=blue}
\DeclareNameAlias{sortname}{last-first}
\DeclareMathOperator*{\argmin}{arg\,min}
\newcolumntype{L}{>{$}l<{$}} % math-mode version of "l" column type
\def\mathbi#1{\textit{ #1}}
\def\mathB#1{\textbf{ #1}}
\def\E{\text{E}}
\mathtoolsset{showonlyrefs=true}

@@

It is desirable that forecasts, whether point forecasts or probabilistic forecasts, should in some sense respect aggregation constraints.  We follow other authors in describing this property as {\em coherence}.   
%While coherent point forecasts have been discussed many times previously, the definitions of coherence previously given are vague and are not easily extended to the situation of probabilistic forecasting.

We now provide new definitions for coherent forecasts in terms of vector spaces that give a geometric understanding of the problem thus facilitating the development of the reconciliation techniques of section~\ref{sec:reconciliation}.

\begin{definition}[Coherent subspace]
Let an $n$-dimensional time series $\bm{y}_t \in \mathbb{R}^n$ be subject to the linear aggregation constraint $\bm{y}_t = \bm{S}\bm{b}_t$, where $\bm{b}_t \in \mathbb{R}^m$ and $\bm{S}$ is an $n \times m$ constant matrix. The $m$-dimensional subspace $\mathfrak{s}\subset \mathbb{R}^n$ that is spanned by the columns of $\bm{S}$, i.e. $\mathfrak{s}=\mbox{span}(\bm{S})$, is defined as the {\em coherent space}. 
\end{definition}

We will also denote the $n\times(n-m)$ orthogonal complement of $\bm{S}$ as $\bm{S}_{\perp}$, where $\mathfrak{s}=\mbox{span}\left(\bm{S}_{\perp}\right)$ is the nullspace of $\bm{S}$
